Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2021-01-13 xrb2/paper.tex
minor changes

The $u$-$\rho$ phase plot in Figure~\ref{fig:urho_hot} shows that the horizontal velocity for the $T_{\rm star} = 3\times10^8$~K is sufficiently  \MarginPar{should this say "significantly"?} greater in magnitude than for the two cooler runs. The $u$-$v$ plot in Figure~\ref{fig:uv_hot} further demonstrates this, as again we see that the magnitude of the velocity in the vertical direction of the flame for the hottest run is also significantly larger. This motion therefore most likely corresponds to the vortical motion rather than to the propagation of the flame itself, something which is further supported by the fact that the velocity magnitude is 2-3 orders of magnitude greater than the flame speeds listed in Table~\ref{table:flame_speeds}. Also of interest in these plots is that the coolest run does not seem to have developed the characteristic vortex structure at the burning front (i.e. where $\dot{e}_{\rm nuc}$ is greatest) that can be clearly seen for the hotter runs at this time ($40~\mathrm{ms}$). As can be seen in Figure~\ref{fig:uv} (which was plotted at $100~\mathrm{ms}$), this does develop more at later times. Similar to what saw when comparing the runs with different rotation rates, it would therefore appear that it takes longer for the flame to develop when $T_{\rm star}$ is cooler.

@@

We ran a number of simulations of laterally propagating flames in XRBs in order to explore the effects and rotation and thermal structure. We found that increasing the rotation rate increased the energy generation rate within the flame, enhancing its propagating \MarginPar{I thought the increased rotation rate enhanced nuclear burning, but suppressed flame propagation?}. This is likely due to greater confinement of the flame from the increased Coriolis force. We explored several models with different crustal temperatures, to determine what effects mechanisms such as higher accretion rates, crustal heating and shallow heating may have on flame propagation. We found that increasing the temperature of the crust significantly enhanced the flame propagation. This we believe to be because a cooler crust allows heat to more efficiently be transferred from the flame itself, therefore reducing the flame's temperature, slowing burning and consequently the reducing its propagation speed. We saw that if the crust temperature was too high, then instead of a flame, the atmosphere would burn stably. This is reminiscent of what is seen for neutron stars with accretion rates exceeding the Eddington luminosity.

>>>>

The $u$-$\rho$ phase plot in Figure~\ref{fig:urho_hot} shows that the horizontal velocity for the $T_{\rm star} = 4\times10^8$~K is significantly greater in magnitude than for the cooler runs. The $u$-$v$ plot in Figure~\ref{fig:uv_hot} further demonstrates this, as again we see that the magnitude of the velocity in the vertical direction of the flame for the hottest run is also significantly larger. This motion therefore most likely corresponds to the vortical motion rather than to the propagation of the flame itself, something which is further supported by the fact that the velocity magnitude is two to three orders of magnitude greater than the flame speeds listed in Table~\ref{table:flame_speeds}. Also of interest in these plots is that the coolest run does not seem to have developed the characteristic vortex structure at the burning front (i.e. where $\dot{e}_{\rm nuc}$ is greatest) that can be clearly seen for the hotter runs at this time ($40~\mathrm{ms}$). As can be seen in Figure~\ref{fig:uv} (which was plotted at $100~\mathrm{ms}$), this does develop more at later times. Similar to what saw when comparing the runs with different rotation rates, it would therefore appear that it takes longer for the flame to develop when $T_{\rm star}$ is cooler.

@@

We ran a number of simulations of laterally propagating flames in XRBs in order to explore the effects and rotation and thermal structure. We found that increasing the rotation rate increased the energy generation rate within the flame, enhancing its propagation \MarginPar{I thought the increased rotation rate enhanced nuclear burning, but suppressed flame propagation?}. This is likely due to greater confinement of the flame from the increased Coriolis force. We explored several models with different crustal temperatures, to determine what effects mechanisms such as higher accretion rates, crustal heating and shallow heating may have on flame propagation. We found that increasing the temperature of the crust significantly enhanced the flame propagation. This we believe to be because a cooler crust allows heat to more efficiently be transferred from the flame itself, therefore reducing the flame's temperature, slowing burning and consequently the reducing its propagation speed. We saw that if the crust temperature was too high, then instead of a flame, the atmosphere would burn stably. This is reminiscent of what is seen for neutron stars with accretion rates exceeding the Eddington luminosity.
